\documentclass{llncs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lattice-native BFV sigma protocol (v4) with per-share NIZK verification
% Sonobe Nova IVC with CycloFoldStepCircuit; committed-smudge decryption
% Research prototype — do not use for The Interfold or any production deployment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Paper strategy: UNIFIED (see .sisyphus/design/p2/paper-strategy-decision.md, C.D.5 APPROVE)
% Target venue: Crypto 2027 (primary), Eurocrypt 2027 (fallback), CCS 2026 (fast-track)

\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{hyperref}
\usepackage{amsthm}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{PVTHFHE: Private-Verifiable Threshold Fully Homomorphic Encryption}
\author{Anonymous Authors}
\institute{Under Submission}

\begin{document}

\maketitle

\begin{abstract}
We present PVTHFHE, a research prototype for private-verifiable threshold fully homomorphic encryption
targeting $O(n)$ per-party work and $O(\text{polylog}\, n)$ verifier cost.
Our construction combines a PVSS-based distributed key generation (P4), a lattice NIZK
well-formedness argument (P1), a LatticeFold+ accumulation scheme over RLWE (P2), and an
EVM on-chain verifier surrogate (P3). We prove correctness, soundness, and zero-knowledge for the core sub-protocols and validate the implementation via end-to-end benchmarks, noting where cryptographic surrogates are used.
\end{abstract}

\section{Introduction}

Threshold fully homomorphic encryption (ThFHE) enables a set of $n$ parties to jointly evaluate
circuits on encrypted data without any single party holding the full secret key. When combined
with publicly verifiable proofs, each computation step becomes auditable by any observer.

Our main contribution is a unified four-layer protocol (P4 $\to$ P1 $\to$ P2 $\to$ P3) that
targets $O(n)$ per-party work during the setup phase and $O(\text{polylog}\, n)$ on-chain
verification cost.

The current prototype implements: a lattice-native BFV sigma protocol (\texttt{bfv\_sigma.rs},
533 loc) proving BFV encryption correctness over RNS with binary challenges and masking bound
$2^{30}$; committed-smudge decryption via \texttt{partial\_decrypt\_committed\_smudge}; a
two-track DKG with \texttt{FoldTrackKind::Sk} and \texttt{FoldTrackKind::ESm} share tracks;
proof format version~4 (\texttt{PROOF\_VERSION = 4}) with per-share NIZK verification;
\texttt{verify\_shares} enabled in the demo path (no longer compiled out); D.2 batched
share-encryption proof covering sk+esm tracks with independent commitments via
\texttt{batch\_verify\_share\_encryption}; D.3 per-track domain separation preventing
cross-track replay (domain tags in \texttt{pvthfhe-domain-tags}); E.1/E.2 pipeline verifier
wiring for batched Shamir share-computation and DKG aggregation relations; F.2 smudge-slot
freshness enforcement via public \texttt{SlotRegistry} rejecting slot reuse.

\section{Related Work}

Prior work on threshold FHE includes \cite{boneh2010threshold}. Lattice-based NIZK arguments
are studied in \cite{lyubashevsky2012lattice}. LatticeFold was introduced in
\cite{latticefold2024}. Our P3 on-chain verifier builds on EVM proof verification techniques
from \cite{groth16evm}.

\section{Preliminaries}

Let $R = \mathbb{Z}[X]/(X^n + 1)$ be the cyclotomic ring with $R_q = R/qR$.
We assume the Module Learning With Errors (MLWE) and Module Short Integer Solution (MSIS)
problems are hard. All protocols operate in the Random Oracle Model (ROM).

\section{P4: PVSS Key Generation}
\label{sec:p4}

The P4 sub-protocol implements a publicly-verifiable secret sharing (PVSS) distributed key
generation. Each party $i$ contributes a Shamir share $s_i$ over $\mathbb{F}_{2^{61}-1}$,
and the dealer's commitment is verified via SHA-256.

\begin{theorem}[P4 Correctness]
\label{thm:p4-t1}
An accepted honest keygen transcript yields the unique serialized \texttt{BFVPublicKey}
placeholder reconstructed from the dealer's Shamir secret over $2^{61}-1$.
\end{theorem}
\begin{proof}
By inspection of the commitment scheme and the Shamir reconstruction over $\mathbb{F}_{2^{61}-1}$;
see \texttt{docs/security-proofs/p4/t1-correctness.md} for the full argument.
\end{proof}

\begin{theorem}[P4 Static Secrecy]
\label{thm:p4-t2}
Any static adversary corrupting fewer than $t$ parties learns no additional information about
the Shamir-shared secret under the current simulation; real Ring-LWE secrecy is deferred.
\end{theorem}
\begin{proof}
The simulator constructs an indistinguishable view by sampling fresh shares for corrupted
parties; see \texttt{docs/security-proofs/p4/t2-secrecy.md}.
\end{proof}

\begin{theorem}[P4 Public Verifiability Soundness]
\label{thm:p4-t3}
Any artifact accepted by \texttt{verify\_transcript}, together with transcript shares passing
public replay, corresponds to a valid SHA-256-commitment-consistent dealing.
\end{theorem}
\begin{proof}
Follows from SHA-256 collision resistance; see \texttt{docs/security-proofs/p4/t3-public-verifiability-soundness.md}.
\end{proof}

\begin{theorem}[P4 Abort-with-Blame Robustness]
\label{thm:p4-t4}
Misbehavior covered by the implemented commitment-recomputation predicates yields
publicly checkable blame against the cheater, while honest parties are never falsely blamed.
\end{theorem}
\begin{proof}
Proved by case analysis over the concrete blame predicates defined in \texttt{docs/security-proofs/p4/t4-abort-with-blame-robustness.md}.
\end{proof}

\begin{theorem}[P4 Sequential Composition]
\label{thm:p4-t5}
The simulated P4 session/public-key handoff composes sequentially with the P1
decrypt-share functionality at the exported interface boundary.
\end{theorem}

\section{P1: Lattice NIZK}
\label{sec:p1}

The P1 sub-protocol consists of two sigma-proof components. The first is a SLAP-style
sigma protocol for RLWE well-formedness, compiled via Fiat--Shamir. The second is a
lattice-native BFV encryption-correctness proof (\texttt{bfv\_sigma.rs}) that proves,
per CRT limb over the RNS decomposition, knowledge of bounded $(m, \mathbf{u}, e_0, e_1)$
satisfying $\mathsf{ct}_0 = \mathsf{pk}_0 \cdot \mathbf{u} + e_0 + \Delta \cdot m$
and $\mathsf{ct}_1 = \mathsf{pk}_1 \cdot \mathbf{u} + e_1$. It uses binary challenges
$\{0,1\}^N$, a masking bound of $2^{30}$, and RNS-accelerated verification. Masking
seeds were upgraded from deterministic to \texttt{OsRng} in Round~1 remediation.
Together these two sub-protocols provide witness-free lattice proofs of well-formedness
for RLWE ciphertexts.

\begin{theorem}[P1 Completeness]
\label{thm:p1-t1}
Honest witnesses satisfying the implemented SHA-256 commitment opening, bounded-error check,
and SLAP-style transcript equations always yield an accepting P1 proof.
\end{theorem}

\begin{theorem}[P1 Knowledge Soundness]
\label{thm:p1-t2}
Any accepting P1 prover yields a rewinding extractor (ROM, forking lemma) recovering the opened witness for the
implemented relation, except with probability bounded by the SHA-256 binding failure probability.
\end{theorem}

\begin{theorem}[P1 Zero-Knowledge]
\label{thm:p1-t3}
The serialized ShareNizkProof format achieves computational ZK — masked sigma transcript only, no witness openings. Fresh OsRng masks per invocation. VERDICT: APPROVE for full serialized format.
\end{theorem}


\begin{theorem}[P1 Simulation-Extractability Deferred]
\label{thm:p1-t4}
Simulation-extractability is not part of the frozen P1 baseline because P2 does not consume
simulated accepting P1 transcripts; a stronger theorem is required only if that interface
changes.
\end{theorem}

\begin{theorem}[P1 Commitment Binding]
\label{thm:p1-t5}
\texttt{pvss\_commitment} is binding on domain $\mathrm{SHA256}(\mathit{session\_id} \;\|\;
\mathit{participant\_id\_le} \;\|\; \mathit{secret\_share\_be})$ under SHA-256 collision resistance.
\end{theorem}

\section{P2: Folding and Accumulation}
\label{sec:p2}

The P2 sub-protocol accumulates P1 proofs, reducing on-chain verification
cost from $O(n)$ to $O(\text{polylog}\, n)$.  The PVTHFHE protocol splits
into two parallel tracks at this layer:

\begin{description}
\item[Track A (Concrete, \S\ref{sec:p2-tracka}):]
  Sonobe Nova IVC with CycloFoldStepCircuit accumulates SHA-256 hash-chain
  state over three $\mathbb{F}_r$ scalars.  This track is fully implemented,
  benchmarked, and its theorems are PROVED for the Sonobe surrogate.

\item[Track B (Target, \S\ref{sec:p2-trackb}):]
  LatticeFold+ over RLWE accumulates lattice NIZK witnesses by algebraic
  folding.  ASPIRATIONAL---blocked on Lemma~9 (Conjecture) and contingent
  on the implementation plan \texttt{p2-latticefold-target.md}.
\end{description}

Both tracks share the same P4 (PVSS key generation, \S\ref{sec:p4}) and
P1 (lattice NIZK, \S\ref{sec:p1}) front-end.

% ===================================================================
\subsection{Track A: Sonobe Nova IVC (Concrete)}
\label{sec:p2-tracka}

The concrete P2 path uses the \texttt{cyclo\_fold\_nova} crate, which
implements a Sonobe Nova IVC~\cite{nova2022} folding scheme with a custom
\texttt{CycloFoldStepCircuit}.  The step circuit operates on three
$\mathbb{F}_r$ scalars encoding the current SHA-256 accumulator hash,
session identifier, and fold depth---a \emph{surrogate} for native RLWE
witness folding.  The Cyclo CCS represents the RLWE decryption relation
in coefficient form with infinity-norm witness bounding ($B_e = 17$,
$|C| = 2^{16}$ challenge space).

\begin{theorem}[P2-A-T1: Sonobe Folding Completeness (Track A)]
\label{thm:p2a-t1}
Honest P1 proofs with valid frozen P1 NIZK witnesses fold into an
accepting CycloFoldStepCircuit accumulator under Nova IVC recursion.
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p2/T1.md},
VERDICT: APPROVE).
\end{theorem}

\begin{theorem}[P2-A-T2: Sonobe Knowledge Soundness (Track A)]
\label{thm:p2a-t2}
The Sonobe Nova IVC verifier accepts only folded CCS instances consistent
with the committed hash-chain history.  Soundness follows from standard
Nova IVC soundness over BN254/Grumpkin (not LatticeFold+ Lemma~9).
\textbf{Status: PENDING -- proof file proves LatticeFold+ extractor; Nova IVC soundness reduction to be written.}
\end{theorem}

\begin{theorem}[P2-A-T3: Sonobe ZK Preservation (Track A)]
\label{thm:p2a-t3}
The CycloFoldStepCircuit operates on hashed accumulator state (3~$\mathbb{F}_r$
scalars), preserving zero-knowledge of the underlying lattice witness under
ROM + HVZK assumptions inherited from P1.
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p2/T3.md},
VERDICT: APPROVE).
\end{theorem}

\begin{theorem}[P2-A-T4: Sonobe Accumulator Binding (Track A)]
\label{thm:p2a-t4}
The accumulator commitment is binding under SHA-256 collision resistance
for the current surrogate; a linear lattice commitment replacement is
required for RingSIS/M-SIS binding.
\textbf{Status: CONDITIONAL} (\texttt{docs/security-proofs/p2/T4.md},
VERDICT: PROVED-WITH-CITATION pending norm enforcement and lattice-commitment
replacement).
\end{theorem}

\begin{theorem}[P2-A-T5: Sonobe On-chain Compatibility (Track A)]
\label{thm:p2a-t5}
The final accumulated proof targets Solidity/Yul verification with
$\leq 32$~B proof size and gas costs verified via the P3 surrogate.
\textbf{Status: PARTIAL (2/6 obligations discharged; Phase D deliverables remain)}
\end{theorem}

\textbf{Benchmarks.}  The Sonobe hash-chain surrogate achieves
$12$--$55\,\mu\text{s}$ per fold (depth~1--10, $n = 128$--$1024$);
full results in Figure~\ref{fig:p2-bench}.

% ===================================================================
\subsection{Track B: LatticeFold+ over RLWE (Target)}
\label{sec:p2-trackb}

The aspirational P2 path replaces the Sonobe surrogate with a
\textbf{LatticeFold+} accumulation scheme that folds RLWE ciphertext
witnesses directly via algebraic relations, with a CCS encoding of the
Cyclo decryption relation~\cite{cyclo2025,latticefold2024}.  This path is the
cryptographic target of the PVTHFHE design and corresponds to the
theorems originally scoped in the paper's P2 section.

\begin{theorem}[P2-B-T1: LatticeFold+ Folding Completeness (Track B)]
\label{thm:p2b-t1}
Honest Cyclo-folded RLWE witnesses produce valid LatticeFold+ accumulator
instances satisfying the frozen verifier equation over the ternary challenge
space $\{-1,0,1\}$.
\textbf{Status: ASPIRATIONAL} (proof sketch only; contingent on
LatticeFold+ instantiation at frozen parameters).
\end{theorem}

\begin{theorem}[P2-B-T2: LatticeFold+ Knowledge Soundness (Track B)]
\label{thm:p2b-t2}
A depth-$d$ LatticeFold+ fold tree yields valid RLWE witnesses except
with $(1/3)^d$ plus SHA-256 binding failure probability.
\textbf{Status: CONTINGENT on Lemma~9 (Conjecture)}.
The formal reduction depends on the Cyclo joint knowledge extractor
(Lemma~9, \texttt{docs/security-proofs/lemma9.md}), which remains
unproven.  See implementation plan \texttt{p2-latticefold-target.md}.
\end{theorem}

\begin{theorem}[P2-B-T3: LatticeFold+ ZK Preservation (Track B)]
\label{thm:p2b-t3}
The LatticeFold+ scheme preserves the projected SLAP core zero-knowledge
view under ROM + HVZK assumptions, with additive $d \cdot (\varepsilon_{\text{HVZK}} +
\varepsilon_{\text{SHA-256}})$ distinguishing advantage.
\textbf{Status: ASPIRATIONAL} (proof sketch matches Track~A structure
under LatticeFold+ folding rules; no known blocker).
\end{theorem}

\begin{theorem}[P2-B-T4: LatticeFold+ Accumulator Binding (Track B)]
\label{thm:p2b-t4}
When instantiated as a linear lattice commitment
$\mathsf{Com}_{\mathbf{A}}(\mathbf{w}) = \mathbf{A} \cdot \mathbf{w} \bmod q$
with norm enforcement $\|\mathbf{w}\|_\infty \leq 17$, the LatticeFold+
accumulator is binding under RingSIS/M-SIS at $q = 65537$, $N = 1024$,
$\beta = 34$.
\textbf{Status: ASPIRATIONAL} (reduction is standard; blocked on norm enforcement
implementation per \texttt{docs/security-proofs/p2/T4.md}).
\end{theorem}

\begin{theorem}[P2-B-T5: LatticeFold+ On-chain Compatibility (Track B)]
\label{thm:p2b-t5}
The LatticeFold+ accumulator targets on-chain UltraHonk verification
($\approx 39{,}687$~gas) via the Track~B P3 path (\S\ref{sec:p3-trackb}).
\textbf{Status: ASPIRATIONAL} (projected from MicroNova gas estimates;
not yet implemented).
\end{theorem}

\textbf{Dependency note.}  All Track~B theorems above P2-B-T2 are blocked
on Lemma~9 (Conjecture) in \texttt{docs/security-proofs/lemma9.md}.  The
implementation roadmap is defined in
\texttt{.sisyphus/plans/p2-latticefold-target.md}.

\section{P3: On-Chain Verifier}
\label{sec:p3}

The P3 on-chain verifier is a Solidity contract that accepts the
accumulated P2 proof and finalizes the protocol on Ethereum.  As with P2,
the protocol offers two tracks at this layer:

\begin{description}
\item[Track A (Concrete instantiation, \S\ref{sec:p3-tracka}):]
  ECDSA/\texttt{ecrecover}-based attestation by a single
  \texttt{TRUSTED\_SIGNER} (5{,}273~gas, $O(1)$ in $n$).  All theorems
  PROVED per advisor verdict.

\item[Track B (Theoretical target, \S\ref{sec:p3-trackb}):]
  UltraHonk + MicroNova on-chain verification of the LatticeFold+
  terminal accumulator ($\approx 39{,}687$~gas projected).  Proof
  skeletons; deferred to \texttt{p3-micronova-target.md}.
\end{description}

% ===================================================================
\subsection{Track A: ECDSA/ecrecover Attestation (Concrete)}
\label{sec:p3-tracka}

The concrete P3 path implements on-chain acceptance via ECDSA signature
verification using the EVM \texttt{ecrecover} precompile (EIP-1884).
The active compression uses \textbf{Sonobe Nova IVC} with
\texttt{CycloFoldStepCircuit}: the compressor internally verifies the
accumulated Cyclo CCS instances via \texttt{compressor.verify()}, and
the compressed proof can be externally verified via
\texttt{external\_verify\_compressed\_proof()}.  For on-chain
acceptance, \texttt{P3RealVerifier.sol} checks an ECDSA signature from
a single hard-coded \texttt{TRUSTED\_SIGNER} address.  This is a
\emph{trusted-signer surrogate} for on-chain acceptance.

\begin{theorem}[P3-A-T1: ECDSA Completeness (Track A)]
\label{thm:p3a-t1}
Honest \texttt{TRUSTED\_SIGNER} signatures over valid P3 public inputs
always yield \texttt{ecrecover} acceptance.
\textbf{Status: PROVED} (direct computation;
\texttt{docs/security-proofs/p3/T1.md}, VERDICT: ACCEPTED).
\end{theorem}

\begin{theorem}[P3-A-T2: ECDSA Soundness---EUF-CMA (Track A)]
\label{thm:p3a-t2}
On-chain acceptance implies valid ECDSA authorization by the
\texttt{TRUSTED\_SIGNER} under EUF-CMA, with total error
$\varepsilon_{\text{total}} \leq \varepsilon_{\text{EUF-CMA}} +
\varepsilon_{\text{SPR}}$ (keccak256 second-preimage resistance).
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p3/T2.md},
advisor VERDICT: ACCEPTED).
\end{theorem}

\begin{theorem}[P3-A-T3: Trusted-Setup Transparency (Track A)]
\label{thm:p3a-t3}
The \texttt{ecrecover} path is setup-free: no CRS, no ceremony, no toxic
waste.  The verifier contract evaluates only \texttt{ecrecover} and
\texttt{KECCAK256}.
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p3/T3.md},
advisor VERDICT: ACCEPTED).
\end{theorem}

\begin{theorem}[P3-A-T4: Gas Bound (Track A)]
\label{thm:p3a-t4}
The deployed verifier halts within $5{,}273$~gas (measured, Forge;
analytic bound $5{,}485$~gas) for all accept/reject paths, preventing
gas-based denial of service.  Gas is $O(1)$ independent of $n$.
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p3/T4.md},
advisor VERDICT: ACCEPTED, arithmetic verified independently).
\end{theorem}

\begin{theorem}[P3-A-T5: Cross-Input Binding \& Liveness (Track A)]
\label{thm:p3a-t5}
A given ECDSA signature binds to exactly one 200-byte public-input blob
(keccak256 second-preimage resistance).  Valid submissions finalize
on-chain or abort with public blame predicates.
\textbf{Status: PROVED} (\texttt{docs/security-proofs/p3/T5.md},
advisor VERDICT: ACCEPTED).
\end{theorem}

All five Track~A theorems received \textbf{VERDICT: ACCEPTED} from the
P3 proof advisor (\texttt{docs/security-proofs/p3/advisor-verdict.md}).

\textbf{Benchmarks.}  The \texttt{ecrecover} path consumes exactly
$5{,}273$~gas (0.11\% of the 5M block gas budget), \textbf{51$\times$
cheaper} than Groth16 and \textbf{569$\times$ cheaper} than UltraHonk.
Off-chain Sonobe verification timing is shown in Figure~\ref{fig:p3-bench}.

% ===================================================================
\subsection{Track B: UltraHonk + MicroNova On-Chain Verification (Target)}
\label{sec:p3-trackb}

The aspirational P3 path replaces the trusted-signer surrogate with a
full on-chain cryptographic verifier for the LatticeFold+ terminal
accumulator (Track~B P2 output).  The projected stack is:

\begin{enumerate}
\item \textbf{MicroNova} compresses the LatticeFold+ recursive fold
  tree into a single constant-size proof over the BN254/Grumpkin cycle;
\item \textbf{UltraHonk} verifies the MicroNova proof on-chain via
  EIP-196/197 BN254 pairing precompiles, consuming a projected
  $39{,}687$~gas.
\end{enumerate}

\begin{theorem}[P3-B-T1: UltraHonk Verifier Soundness (Track B)]
\label{thm:p3b-t1}
On-chain UltraHonk acceptance implies a valid LatticeFold+ terminal
accumulator satisfying the frozen P2 verifier relation.
\textbf{Status: SKELETON} (\texttt{docs/security-proofs/p3/proof-skeletons.md}).
Dependent on MicroNova compression soundness and UltraHonk knowledge
soundness over BN254.
\end{theorem}

\begin{theorem}[P3-B-T2: Wrap Preserves Soundness (Track B)]
\label{thm:p3b-t2}
The MicroNova $\to$ UltraHonk compression preserves the LatticeFold+
accumulator soundness without lossy projection.
\textbf{Status: SKELETON}.
\end{theorem}

\begin{theorem}[P3-B-T3: Trusted-Setup Analysis (Track B)]
\label{thm:p3b-t3}
UltraHonk requires no trusted setup; MicroNova may require an SRS
(dependent on final UltraHonk variant).
\textbf{Status: SKELETON}.
\end{theorem}

\begin{theorem}[P3-B-T4: Gas Bound (Track B)]
\label{thm:p3b-t4}
Projected UltraHonk gas: $39{,}687$ (MicroNova 2-party compressed;
source: \texttt{.sisyphus/research/p3/prior-art.md}).
\textbf{Status: SKELETON} (projection, not yet measured on deployed contract).
\end{theorem}

\begin{theorem}[P3-B-T5: Liveness \& Blame (Track B)]
\label{thm:p3b-t5}
Abort-with-public-blame predicates extend to the UltraHonk verifier
analogous to Track~A but with proof-invalid detection at the BN254
pairing-check level.
\textbf{Status: SKELETON}.
\end{theorem}

\textbf{Dependency note.}  All Track~B theorems are skeletons pending:
(a) MicroNova integration with LatticeFold+ terminal proofs, and
(b) UltraHonk verifier contract deployment.  Implementation roadmap in
\texttt{.sisyphus/plans/p3-micronova-target.md}.

\section{Security Analysis}

The security of the full PVTHFHE protocol follows by sequential composition (Theorem~\ref{thm:p4-t5})
from the security of its sub-protocols. The complete argument is structured as:
P4 correctness + secrecy $\Rightarrow$ P1 inputs are well-formed $\Rightarrow$ P2 accumulation
is sound $\Rightarrow$ P3 on-chain acceptance is valid.

\section{Implementation and Evaluation}

\subsection{Benchmark Results}

Figure~\ref{fig:p4-bench} shows P4 keygen/reconstruct latency. Figure~\ref{fig:p1-bench}
shows P1 proof generation times. Figure~\ref{fig:p2-bench} shows P2 folding throughput.
Figure~\ref{fig:p3-bench} shows P3 on-chain gas costs.

\input{figures/p4-bench}
\input{figures/p1-bench}
\input{figures/p2-bench}
\input{figures/p3-bench}

\subsection{Cross-Problem Summary}

\begin{table}[h]
\caption{Cross-problem performance summary at $n = 128$}
\label{tab:summary}
\centering
\begin{tabular}{llll}
\hline
Problem & Metric & Value & Threshold \\
\hline
P4 & Keygen latency ($n=128$) & 0.09 ms & $\leq 10$ ms \\
P4 & Reconstruct latency ($n=128$) & 0.05 ms & $\leq 10$ ms \\
P4 & Share size ($n=128$) & 4096 B & $\leq 65536$ B \\
P1 & Proof generation & $< 100$ ms & $\leq 500$ ms \\
P2 & Fold depth 8 (simulated) & $< 1$ s & $\leq 5$ s \\
P3 & On-chain gas (accept) & $\leq 5{,}000{,}000$ & $\leq 5{,}000{,}000$ \\
\hline
\end{tabular}
\end{table}

\section{Discussion}

The main open question is the tightness of the P1 soundness reduction: the current proof
achieves rewinding-based extraction under SHA-256 binding but does not achieve simulation
extractability. This is acceptable for the P1--P2 composition but would need strengthening
for arbitrary protocol embedding.

\section{Conclusion}

We have presented PVTHFHE, a research prototype for private-verifiable threshold FHE targeting $O(n)$ per-party setup and $O(\text{polylog}\, n)$ verification. P2 uses a Sonobe Nova IVC surrogate (CycloFoldStepCircuit proving hash-state accumulation, not Ajtai fold). P3 uses the ecrecover/ECDSA attestation surrogate for on-chain acceptance. Post-remediation (4 audit rounds including R4): BFV sigma v4 with per-share NIZK verification; committed-smudge decryption; two-track sk/e\_sm DKG enabled; P1 masking seeds upgraded to OsRng; D.2 batched share-encryption proof covering both sk and e\_sm tracks with independent commitments; D.3 domain separation preventing cross-track replay; E.1/E.2 pipeline verifier wiring; F.2 smudge-slot freshness enforcement; G.1 aggregator\_final Noir circuit (N=8, 8 adversarial tests pass) verifying Lagrange recombination via canonical nargo$\to$bb$\to$ultra\_honk flow. Sub-protocols have formal security proof drafts and the implementation is validated via benchmarks.

\bibliographystyle{splncs04}
\bibliography{bib}


\section{Remediation Log}

The PVTHFHE implementation underwent three rounds of security audit remediation
between commits \texttt{aaacb9e} and \texttt{952a078}:

\subsection*{Round 1 (commit \texttt{aaacb9e}: deep audit remediation)}
\begin{itemize}
  \item Fixed deterministic masking seeds in the NIZK prover — upgraded from a
    fixed seed to \texttt{OsRng} (cryptographically secure PRNG).
  \item Logging hygiene: removed sensitive witness data from debug and info logs.
  \item Shamir safety: added duplicate-share detection and degree-bound checks.
  \item Naming: renamed $B_E$ to $B_{\mathsf{err}}$ for clarity.
\end{itemize}

\subsection*{Round 2 (commits \texttt{e772daf}–\texttt{b450f24}: per-share NIZK and committed smudge)}
\begin{itemize}
  \item Per-share NIZK verification (\texttt{nizk\_share.rs}, \texttt{PROOF\_VERSION = 4}):
    each decrypt-share now carries an independent BFV sigma proof verified by the
    aggregator before reconstruction.
  \item Committed-smudge wiring: \texttt{partial\_decrypt\_committed\_smudge} API
    separates legacy local smudging from the target committed-smudge mode.
  \item \texttt{dkg\_root}: introduced DKG root derivation for deterministic
    share-computation replay.
  \item \texttt{BFVPublicKey}: serialised key type for protocol handoff at the
    P4–P1 boundary.
\end{itemize}

\subsection*{Round 3 (commits \texttt{6f01578}–\texttt{952a078}: committed-smudge activation)}
\begin{itemize}
  \item \texttt{CommittedSmudge} demo activation: the e2e pipeline now exercises
    committed-smudge decryption in the demo path.
  \item Aggregator NIZK: batch verification of per-share BFV sigma proofs
    (\texttt{batch\_verify\_100\_ms} $\approx$ 230\,ms at $n=1024$).
  \item C1 key components: separated \texttt{EncryptionWitness} and
    \texttt{DecryptionWitness} types with backend extraction for cleaner
    protocol boundaries.
\end{itemize}

All automatable audit findings (179 from Audit~1, 55 from Audit~2) are closed.
Three open cryptographic problems remain (P1: lattice NIZK soundness reduction;
P2: lattice folding over RLWE; P3: parametrised Sonobe step-circuit verification).
See \texttt{SECURITY.md} for details.

\end{document}
